An objective assessment of point scoring systems in Formula 1 motor racing

### 2023-02-07 inst/j_sports_sci_F1_points.tex
minor journal-specific tweaks
unemphasise tournament theory

\journal{Journal of Economic Behavior and Organization}

@@

\begin{frontmatter}
  \title{An objective assessment of point scoring systems in Formula 1 motor racing}
  \author{Robin K. S. Hankin\fnref{myfootnote}}
\address{AUT University, 55 Wellesley Street, Auckland 1010, New Zealand}

\begin{abstract}
The points scoring system of Formula 1 motor racing is a long-standing
contention among fans and competitors.  The inaugural points system
was $(8,6,4,3,2)$, that is, 8 points to the winner, 6 to second place,
and so on; in 2020 the points system was changed to
$(25,18,15,12,10,8,6,4,2,1)$.  However, it is difficult to assess
statistical nulls using accumulated points.  Here, I use Plackett-Luce
likelihood to identify a ranking for the competitors from the
perspective of tournament theory, this method being amenable to
statistical testing.  I go on to assess a number of reasonable points
systems objectively: in one well-defined statistical sense a Borda
points system is optimal.
\end{abstract}
\begin{keyword}
Reified Bradley-Terry\sep Likelihood\sep Formula 1 motor racing\sep Points systems
\end{keyword}

>>>>

\journal{Journal of Sports Sciences}

@@

\begin{frontmatter}
  \title{An objective assessment of point scoring systems in Formula 1 motor racing}
  \author{Robin K. S. Hankin\fnref{fn1}}
  \address{AUT University, 55 Wellesley Street, Auckland 1010, New Zealand\\
  }

\fntext[fn1]{\url{https://orcid.org/0000-0001-5982-0415}; {\tt hankin.robin@gmail.com}}

\begin{abstract}
The points scoring system of Formula 1 motor racing is a long-standing
contention among fans and competitors.  The inaugural points system
was $(8,6,4,3,2)$, that is, 8 points to the winner, 6 to second place,
and so on; in 2020 the points system was changed to
$(25,18,15,12,10,8,6,4,2,1)$.  However, it is difficult to assess
statistical nulls using accumulated points.  Here, I use Plackett-Luce
likelihood to identify a ranking for the competitors, this method
being amenable to statistical testing.  I go on to assess a number of
reasonable points systems objectively: in one well-defined statistical
sense a Borda points system is optimal.
\end{abstract}
\begin{keyword}
Reified Bradley-Terry\sep Likelihood\sep Formula 1 motor racing\sep Points systems
\end{keyword}
